\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-29 manuscript/manuscript.tex
figure code updated but data not updated yet so figures are not yet correct

\section{Appendix}\label{sec:appendix}
In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block bootstrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of
block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block_normal} and \ref{fig:large_block_gamma}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block_normal}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$.
  }
  \label{fig:large_block_normal}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block_gamma}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $\Gamma(8,1)$.
  }
  \label{fig:large_block_gamma}
\end{figure}

>>>>

\section{Appendix}\label{sec:appendix}
In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block bootstrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of
block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block} and \ref{fig:large_block}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$ and $\Gamma(8,1)$.
  }
  \label{fig:large_block}
\end{figure}

Even for the settings with block sizes that are typically less than
$\sqrt{n}$ such as for $n = 800, X_i \sim N(8, 8)$, and $\tau = 0.5$, our 
algorithm still does not hold its size as demonstrated in 
Figure~\ref{fig:my_setting}, and the block
sizes are still much larger than $l = \lceil n^{1/3} \rceil$, which is often
considered optimal in general.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/my_setting}
  \caption{Q-Q plot of the p-values testing that a length-800 time series with
    Kendall's $\tau = 0.5$
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$.
  }
  \label{fig:my_setting}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/block_dist}
  \caption{Distribution of the selected block sizes using
  \citet{politis2004automatic}'s procedure applied to a length-800 time series with
    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$.
  }
  \label{fig:block_dist}
\end{figure}
